Pushdown Control-Flow Analysis via Refunctionalization (Functional Pearl)

### 2018-02-27 paper.tex
update

%% Title information
\title[Short Title]{Pushdown Control-Flow Analysis via Refunctionalization (Functional Pearl)}         %% [Short Title] is optional;
                                        %% when present, will be used in
                                        %% header instead of Full Title.
\titlenote{with title note}             %% \titlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'
\subtitle{Filling the Gap between Abstracting Abstract Machine and Abstracting Definitional Interpreter}        %% \subtitle is optional
\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'

@@

@@

The paper is organized as follows. 
TODO: add a diagraph on transformations.
Section \ref{background} reviews the background.

\begin{tikzpicture}
  \matrix (m) [matrix of math nodes, row sep=3em, column sep=3em]
    { abstracting abstract machines & A  & B  & C  & 0 \\
      abstract machines & A' & B' & C' & 0 \\ };
  { [start chain] \chainin (m-1-1);
    \chainin (m-1-2);
    { [start branch=A] \chainin (m-2-2)
        [join={node[right,labeled] {\eta_1}}];}
    \chainin (m-1-3) [join={node[above,labeled] {\varphi}}];
    { [start branch=B] \chainin (m-2-3)
        [join={node[right,labeled] {\eta_2}}];}
    \chainin (m-1-4) [join={node[above,labeled] {\psi}}];
    { [start branch=C] \chainin (m-2-4)
        [join={node[right,labeled] {\eta_3}}];}
    \chainin (m-1-5); }
  { [start chain] \chainin (m-2-1);
    \chainin (m-2-2);
    \chainin (m-2-3) [join={node[above,labeled] {\varphi'}}];
    \chainin (m-2-4) [join={node[above,labeled] {\psi'}}];
    \chainin (m-2-5); }
\end{tikzpicture}

@@

There are two main reasons to use a real-world language:
1) The code does not diminish the accuracy of the material
than formal and mathematical notations, 
which are heavily used in other papers in static analysis or semantics.
The Scala code in this paper can be easily back-translated into formal notations.
2) As a functional pearl, the code in this paper is executable with only few changes, 
which make it particularly fit for presenting syntactical transformations on abstract
interpreters.

>>>>

%% Title information
\title[Short Title]{Pushdown Control-Flow Analysis via Refunctionalization (Functional Pearl)}         %% [Short Title] is optional;
                                        %% when present, will be used in
                                        %% header instead of Full Title.
\titlenote{with title note}             %% \titlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'
\subtitle{Filling the Gap between Abstracting Abstract Machines and Abstracting Definitional Interpreters}        %% \subtitle is optional
\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'

@@

boardly speaking, AAM and ADI they are both abstract interpreters.

@@

The paper is organized as follows. 
Section \ref{background} reviews the background.

\begin{tikzpicture}
  \matrix (m) [matrix of math nodes, row sep=3em, column sep=3.7em]
    { 
      \begin{smallmatrix} \text{abstracting} \\ \text{abstract} \\ \text{machines} \end{smallmatrix} & 
      \begin{smallmatrix} \text{big-step} \\ \text{abstracting} \\ \text{abstract} \\ \text{machines} \end{smallmatrix}  & 
      \begin{smallmatrix} \text{disentangled}  \\ \text{abstracting} \\ \text{abstract} \\ \text{machines} \end{smallmatrix} & 
      \begin{smallmatrix} \text{refunctionalized}  \\ \text{abstracting} \\ \text{abstract} \\ \text{machines} \end{smallmatrix} & 
      \begin{smallmatrix} \text{abstracting} \\ \text{definitional} \\ \text{interpreters} \end{smallmatrix}  \\
      \begin{smallmatrix} \text{abstract} \\ \text{machines} \end{smallmatrix} & 
        &
      %\begin{smallmatrix} \text{big-step} \\ \text{abstract} \\ \text{machines} \end{smallmatrix}  & 
        &
      %\begin{smallmatrix} \text{disentangled} \\ \text{abstract} \\ \text{machines} \end{smallmatrix} & 
        &
      %\begin{smallmatrix} \text{refunctionalized} \\ \text{abstract} \\ \text{machines} \end{smallmatrix} & 
      \begin{smallmatrix} \text{definitional} \\ \text{interpreters} \end{smallmatrix} \\ 
    };

  { 
    [start chain] \chainin (m-1-1);
    \chainin (m-1-2) [join={node[above,labeled] {\text{fusion}}}];

    \chainin (m-1-3) [join={node[above,labeled] {\text{disentangling}}}];

    \chainin (m-1-4) [join={node[above,labeled] {\text{refunc.}}}];

    \chainin (m-1-5) [join={node[above,labeled] {\text{monadify}}}];
  }
  { 
    [start chain] 
    \chainin (m-2-1);
    { [start branch=A] \chainin (m-1-1)
      [join={node[left, labeled] {\alpha}}];
    }
  }
    %\chainin (m-2-2);
    %\chainin (m-2-3);
    %\chainin (m-2-4);
  {
    [start chain] 
    \chainin (m-2-5); 
    { [start branch=B] \chainin (m-1-5)
      [join={node[left, labeled] {\alpha}}];
    }
  }
\end{tikzpicture}

@@

There are two main reasons we use a real-world language:
1) The code does not diminish the accuracy of the material
than formal and mathematical notations, 
which are heavily used in other static analysis or semantics papers.
The Scala code in this paper can be easily back-translated into formal notations.
2) As a functional pearl, the code in this paper is executable with only few changes, 
which make it particularly fit for presenting syntactical transformations on abstract
interpreters.
